AFQ-Insight

### 2019-12-01 reports/manuscript/sections/results.tex
Reorganizing plots a bit.

The WH dataset used for continuous regression contains data from 76 healthy
subjects, ranging between 6 years and 50 years of age
\cite{yeatman2014lifespan}. In this case, biological age was used as the
predicted variable ($y$ in equation \ref{eq:lm}). SGL was fit to
tractometry-extracted features: FA and MD in 20 major brain tracts, with each
tract divided into 100 nodes. To evaluate the fit of the model, we used a nested
cross-validation procedure. In this procedure, batches of subjects are held out.
For each batch (or fold), the model is fully fit without this data. Then, once
the parameters are fixed, the model is inverted to predict the ages of held out
subjects based on the linear coeffiecients and the static non-linearity. data is
held out, and a model age was predicted using a model that was fit without that
subject. This scheme automatically finds the right level of regularization and
fits the coefficients to the ill-posed linear model, while guarding against
overfitting. SGL accurately predicts the age of the subjects in this procedure,
with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}). This
is lower than the results of a recent study that predicted age in a large
sample, based on diffusion MRI features \cite{Richard2018-ux}. The model weights
in this case are distributed over many different tracts and dMRI tissue
properties (Figure \ref{fig:regress-beta}). This demonstrates that SGL is not
coerced to produce overly sparse results when a more accurate model requires a
dense selection of features.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{regression_residuals.png}
    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted age of each individual (on the abscissa) and true age (on the ordinate), an accurate prediction falls close to the $y=x$ line (dashed). The mean absolute error in this case  is 3.6 years and, the coefficient of determination $R^2=0.3$. Right: Standardized residuals (on the abscissa) as a function of the true age (on the ordinate). Predictions are generally more accurate for younger individuals.
    }
    \label{fig:regress-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.3\textwidth]{regression_beta_annotated.pdf}
    \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with the anterior up. The left cingulum cingulate (A) and forceps minor (B) are highlighted. Right: the FA (in shades of blue and green) and the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps minor.
    }
    \label{fig:regress-beta}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.65\textwidth]{classification_probs.png}
    \caption{{\bf Prediction of ALS status.}
        Classification probabilities for each subject's ALS diagnosis. Controls
        are on the left while patients are on the right. Predicted controls are in blue
        and predicted patients are in red. Thus, false positive are represented as red
        dots on the left, while false negatives are represented as blue dots on the
        right. The SGL algorithm achieves 93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006
        ROC AUC}
    \label{fig:class-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\textwidth]{classification_beta_bupu.png}
    \caption{{\bf Feature importance for prediction of ALS status.}
        SGL coefficients are presented on a skeleton of the major tracts. The
    brain is oriented with the right hemisphere to our left and anterior out of
    the page. As expected large negative coefficients are in the FA of the
    corticospinal tract (and particularly right CST, here to the left)}
    \label{fig:class-beta}
\end{figure}

@@

\begin{itemize}
  \item Classification
    \begin{itemize}
      \item Insert figure showing weights as they relate to tract differences visible in the browser
    \end{itemize}
\end{itemize}

>>>>

To test the performance of SGL in tractometry data in a continuous regression
task, we focus here on the prediction of biological age from the tractometry
data. Prediction of ``brain age'' is a commonly undertaken task. This is both
because it operates on a natural scale, with meaningful and easily understood
units, as well as because predictions of brain age, and deviations from accurate
prediction are diagnostic of overall brain age \ariel{citation needed}. The WH
dataset used here contains data from 76 healthy subjects, ranging between 6
years and 50 years of age \cite{yeatman2014lifespan}. In this case, biological
age was used as the predicted variable ($y$ in equation \ref{eq:lm}). SGL was
fit to tractometry-extracted features: FA and MD in 20 major brain tracts, with
each tract divided into 100 nodes. To evaluate the fit of the model, we used a
nested cross-validation procedure. In this procedure, batches of subjects are
held out. For each batch (or fold), the model is fully fit without this data.
Then, once the parameters are fixed, the model is inverted to predict the ages
of held out subjects based on the linear coeffiecients and the static
non-linearity. data is held out, and a model age was predicted using a model
that was fit without that subject. This scheme automatically finds the right
level of regularization and fits the coefficients to the ill-posed linear model,
while guarding against overfitting. SGL accurately predicts the age of the
subjects in this procedure, with a mean absolute error of 3.6 years (Figure
\ref{fig:regress-results}, left panel). This is lower than the results of a
recent study that predicted age in a large sample, based on diffusion MRI
features \cite{Richard2018-ux}. Nevertheless, older subjects have higher
residual variance, reflecting the automatically-chosen log-transformation and
implying that brain age becomes more difficult to predict as we age
chronologically (\ref{fig:regress-result}, right panel). The model weights are
distributed over many different tracts and dMRI tissue properties (Figure
\ref{fig:regress-beta} left). This demonstrates that SGL is not coerced to
produce overly sparse results when a more accurate model requires a dense
selection of features. Furthermore, looking closer at a selection of tracts
where high coefficients are found demonstrates that diffusion properties (FA, in
this case) are different in different age groups in parts of the tracts where
these higher coefficients are found (Figure \ref{regress-beta} right).

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{regression_residuals.png}
    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted age of each individual (on the abscissa) and true age (on the ordinate), from the test splits (i.e., when each subject's data was held out in fitting the model); an accurate prediction falls close to the $y=x$ line (dashed). The mean absolute error in this case is 3.6 years and, the coefficient of determination $R^2=0.3$. Right: Standardized residuals (on the abscissa) as a function of the true age (on the ordinate). Predictions are generally more accurate for younger individuals.
    }
    \label{fig:regress-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.3\textwidth]{regression_beta_annotated.pdf}
    \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with anterior facing up, and right hemisphere on the right. The $\hat{\beta}$ coefficients displayed in blue (negative) to red (positive) are for measurements of FA along the tracts. The left cingulum cingulate (A) and forceps minor (B) are highlighted. Right: the FA (in shades of blue and green) and the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps minor.
    }
    \label{fig:regress-beta}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.45\textwidth]{classification_probs.png}
    \includegraphics[width=0.45\textwidth]{classification_beta_bupu.png}

    \caption{{\bf Prediction of ALS status.}
        Left: Classification probabilities for each subject's ALS diagnosis.
        Controls are on the left while patients are on the right. Predicted
        controls are in blue and predicted patients are in red. Thus, false
        positive are represented as red dots on the left, while false negatives
        are represented as blue dots on the right. The SGL algorithm achieves
        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
        coefficients are presented on a skeleton of the major tracts. The brain
        is oriented with the right hemisphere to our left and anterior out of
        the page. As expected large negative coefficients are in the FA of the
        corticospinal tract (and particularly right CST, here to the left)}
    \label{fig:class-results}
\end{figure}

@@
